TBD

### 2021-03-23 outputs/paper/paper.Rmd
Updated formualae in model section to LaTeX proper eq's

## Formulae

@@

```{r s10modelcheck, echo - FALSE, warning = FALSE, message = FALSE}
### S10/Table 3 (main result)

>>>>

## Formulae
Table 1 (column 1) + Table 3:
$$
Y \sim \beta_0 + \beta_1X_1 + \epsilon
$$
Table 1 (column 2):

$$
Y \sim \beta_0 + \beta_1X_1 + \beta_2X_2 + \beta_3X_3 + \beta_4X_4 + \beta_5X_5 + \beta_6X_6 + \epsilon
$$

Table 2:

$$
Y \sim \beta_0 + \beta_1X_1 + \beta_2X_2 + \epsilon
$$

@@

```{r s10modelcheck, echo = FALSE, warning = FALSE, message = FALSE}
### S10/Table 3 (main result)
